Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-03-02 paper/EDA.qmd
Assumption check completed

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Assumption Check for Time taken after taking the Drug"

# Fit ANOVA Model
model <- aov(game_after ~ drug, data = clean_data)

# Check Model Assumptions
check_model(model, check = c("normality", "homogeneity"))

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 9
#| fig.height: 8
#| dpi: 300
#| fig-cap: "Assumption Check for Time taken before taking the Drug"

# Fit ANOVA Model
model_b <- aov(game_before ~ drug, data = clean_data)

# Check Model Assumptions
check_model(model_b, check = c("normality", "homogeneity"))

@@

```{r}
#| echo: false
#| warning: false
#| message: false
# Boxplot to visualize the distribution of `game_after`
ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
  geom_boxplot() +
  ggtitle("Boxplot of Game After Scores by Drug and Dosage Level")

@@

anova_model <- aov(game_after ~ drug + dosage_level, data = clean_data)
summary(anova_model)
# install.packages("ggpubr")
# QQ plot for residuals
ggqqplot(residuals(anova_model))

# Sharpio Test
shapiro.test(residuals(anova_model))
# p-value is greater than 0.05 we fail to reject Ho implies Normality

@@

model_cards_dose <- aov(cards_after ~ drug + dosage_level, data = clean_data)
shapiro.test(residuals(model_cards_dose))
ggqqplot(residuals(model_cards_dose))
```

>>>>

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Time Taken for Memory Game after taking Drugs"

# Boxplot to visualize the distribution of time taken to solve Memory game after taking pain killers
ggplot(clean_data, aes(x = drug, y = game_after, fill = dosage_level)) +
  geom_boxplot() +
  ggtitle("Time Taken for Memory Game after taking Drugs")

@@

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Time Taken for Memory Game after taking Drugs"

# we fit One-Way ANOVA Model for our research question 1
model_1 <- aov(game_after ~ drug, data = clean_data)

# Check Model Assumptions
check_model(model_1, check = c("normality", "homogeneity"))

summary(model_1)
```

```{r}
#| echo: false
#| warning: false
#| message: false
# bartlett_test_part1 <- bartlett.test(game_after ~ drug, data = clean_data)
# print(bartlett_test_part1)
```

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Residual Plot Model 1"

# QQ plot for Normality assumption
ggqqplot(residuals(model_1)) +
  ggtitle("QQ Plot for Residuals Model 1")

# Shapiro-Wilk Tet
# shapiro_test <- shapiro.test(residuals(model_1))
# print(shapiro_test)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Normality & Homegenity"

# Corrected Two-Way ANOVA Model for our reseearch question 2
model_2 <- aov(game_after ~ drug + dosage_level, data = clean_data)

# Check Model Assumptions
check_model(model_2, check = c("normality", "homogeneity"))

@@

# Shapiro-Wilk Test for Normality of Residuals
# shapiro_test_part2 <- shapiro.test(residuals(model_part2))
# print(shapiro_test_part2)

@@

```{r}
#| echo: false
#| warning: false
#| message: false
#| fig.width: 6
#| fig.height: 4
#| fig-cap: "Residual Plot Model"

# QQ plot for residuals of Part 2
ggqqplot(residuals(model_2)) +
  ggtitle("QQ Plot Two-Way ANOVA Model")
